Demanding resources: Converging perceptions of challenge and resource characteristics

### 2023-06-13 SIOP2024/SIOP2024convergence.Rmd
siop revisions working

*RQ1*: Do people distinguish between challenge and hindrance stressors?

@@

*RQ2*: Characteristics perceived as challenges are also commonly viewed as resources.

Although we argue that the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others. For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge. O\*Net has different levels of abstraction with regard to the nature of job characteristics. We will be exploring a mid-level abstraction with seven different characteristic scales.

*RQ3*: The association between challenging and resourceful characteristics is moderated by type of characteristic.

>>>>

*RQ1 is a good idea for A DIFFERENT PAPER. Do ICC(1,1)*
*RQ1*: Do people distinguish between challenge and hindrance stressors?

@@

*RQ1*: Are job characteristics perceived as challenges are also commonly viewed as resources?  
Although we argue that the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others. For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge. O\*Net has different levels of abstraction with regard to the nature of job characteristics. We will be exploring a mid-level abstraction with seven different characteristic scales.

*RQ2*: Is the association between challenge and resource characteristics moderated by type of characteristic?
